Analysis of split plot design using MCMCglmm

### 2020-05-19 README.Rmd
Correct link in README

The files at the URL above will generate the results as found in the
publication. The files hosted at
<https://github.com/adamhsparks/rice_awd_pests> are the development
versions and may have changed since the report was published.

>>>>

The files at the URL above will generate the results as found in the
publication. The files hosted at
<https://github.com/adamhsparks/rice_AWD_ShB_analysis> are the development
versions and may have changed since the report was published.
